\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{latexsym}
\usepackage{fontawesome5}

\definecolor{blue}{RGB}{0,0,255}

\pagestyle{empty}

\begin{document}

\begin{center}
    \textbf{\LARGE Matheus Felipe Neves Campos Cardoso} \\
    Backend Developer 
\end{center}

\begin{minipage}[t]{0.60\textwidth}
    \section*{\faUser \space Professional Summary}
    Backend Developer with skills in NodeJS, Python, and Java, as well as relational databases like SQL Server, Hadoop, and Athena/S3. Currently working as a Data Analyst at Itaú, I am enhancing my Backend skills through courses and personal projects.\\\\
    I have knowledge in Algorithms, Data Structures, and I am seeking opportunities to expand my experience as a Developer.

    \section*{\faBriefcase \space Professional Experience}
        \textbf{Itaú Unibanco} \\
        \textit{Period:} Feb/21 - Present \\
        \textit{Position:} Intern $\rightarrow$ Data Analyst

        \begin{itemize}[left=0pt]
            \item Created Python scripts and Alteryx workflows for data modeling, automation, and specialization.
            \item Ingested and maintained databases in Hadoop/SQL/SAS/ATHENA + S3 environments.
            \item Built dashboards for data visualization in Tableau. \\*
        \end{itemize}

        \textbf{Itgoal} \\
        \textit{Period:} Mar/20 - Nov/20 \\
        \textit{Position:} Backend Intern

        \begin{itemize}[left=0pt]
            \item Developed automations and scripts for Zoho systems.
            \item Built dashboards using SQL in Zoho Analytics.
            \item Integrated APIs.
            \item Provided Helpdesk Support.
        \end{itemize}

    \section*{\faBook \space Academic Background}
        \textbf{SENAC University Center} \\
        \textit{Degree:} Bachelor of Computer Engineering \\
        \textit{Period:} 2019 - 2024
\end{minipage}%
\hfill
\begin{minipage}[t]{0.3\textwidth}
    \section*{\faAddressCard \space Contact}
    
    \begin{tabular}{l l}
        \textbf{Phone:} & \href{tel:+5511996315436}{\textcolor{blue}{+55 (11) 99631-5436}} \\
        \textbf{Email:} & \href{mailto:matheus.felipe337@gmail.com}{\textcolor{blue}{matheus.felipe337@gmail.com}} \\
        \textbf{LinkedIn:} & \href{https://www.linkedin.com/in/matheus-felipe-neves/}{\textcolor{blue}{/in/matheus-felipe-neves/}} \\
        \textbf{GitHub:} & \href{https://github.com/ndrake337}{\textcolor{blue}{github.com/ndrake337}}
    \end{tabular}

    \section*{\faTerminal \space Skills}

    \begin{itemize}[left=0pt, label={}]
        \item Programming Languages:
        \begin{itemize}
            \item JavaScript/Typescript; Python, Java
            \item SQL, SAS
        \end{itemize}
        
        \item Frameworks:
        \begin{itemize}
            \item Spring Boot, Nest.JS, Express, Fastify
        \end{itemize}
        
        \item Databases:
        \begin{itemize}
            \item MySQL, SQL Server, Postgres
            \item Hadoop, Athena, S3
        \end{itemize}
        
        \item Code Versioning:
        \begin{itemize}
            \item Git
        \end{itemize}
        
        \item Agile Development:
        \begin{itemize}
            \item Scrum
            \item Clean Architecture
            \item Solid
            \item DDD
        \end{itemize}
    \end{itemize}

    \section*{\faLanguage \space Languages}
    \begin{itemize}
        \item \textbf{Portuguese:} Native
        \item \textbf{English:} Advanced
    \end{itemize}

    \section*{\faCertificate \space Certificates}
    \begin{itemize}[left=0pt]
        \item Practitioner - D\&A Foundation - Itaú Unibanco -
        \item Curso de Java - RocketSeat (2023)
        \item Clean Code - RocketSeat (2023)
    \end{itemize}
\end{minipage}

\end{document}